\maketitle
\marginnote{srb2242@gmail.com}
\marginnote{+1 650 338 6530}
\marginnote{\href{http://www.simonbox.info}{simonbox.info}}
\marginnote{\href{https://www.linkedin.com/in/simon-box-8090379a/}{linkedin.com/in/simon-box-8090379a}}
\marginnote{\href{https://github.com/SimonBox}{github.com/SimonBox}}
\marginnote{\href{https://sourceforge.net/u/srb2242/profile/}{sourceforge.net/u/srb2242}}


\begin{abstract}
Engineer with specialization in Simulation and Machine Learning and especially applications that concern both: sim-to-real, synthetic training data, autonomous vehicle simulation.
\end{abstract}

\section{Experience}

\subsection{2017- Senior Director of Simulation and Offline Testing at Aurora}

\marginnote{\href{https://aurora.tech}{aurora.tech}}
\marginnote{\href{https://www.businessinsider.com/aurora-ceo-virtual-tests-better-than-real-world-tests-2020-2}{Business Insider article}}
\marginnote{\href{https://aurora.tech/blog/scaling-simulation}{Scaling simulation}}
\marginnote{\href{https://aurora.tech/blog/virtual-testing-the-invisible-accelerator}{Virtual testing}}
\marginnote{\href{https://aurora.tech/blog/online-to-offline}{Online to offline}}

As Senior Director I serve a team of $\sim\!\!100$ engineers, which we grew from just 2 when I joined in 2017. Our team develops tooling that has allowed Aurora to move to a development workflow driven entirely by by simulation. Simulation happens at a large scale at Aurora with more than 5m sims run daily. See the margin links for public blog posts and a media article where Aurora's CEO discusses Simulation.

\subsection{2016-2017 Head of Autopilot Simulation at Tesla}

\marginnote{\href{https://www.tesla.com/autopilot}{tesla.com/autopilot}}
As Autopilot Sim lead I served a team of $\sim\!\!20$ engineers, which we grew from just 2 when I joined in 2016. The team produced a number of simulation tools that helped accelerate development and contributed to the launch of the "Hardware 2.0" version of Autopilot.

\subsection{2008-2016 New frontiers research fellow, University of Southampton}

\marginnote{Some publications:}
\marginnote{\href{https://royalsocietypublishing.org/doi/full/10.1098/rsos.140211}{AI intersection conrol}}
\marginnote{\href{https://eprints.soton.ac.uk/336298/1/tdpaper2012\%2520\%25281\%2529.pdf}{RL in traffic sim}}
\marginnote{\href{https://eprints.soton.ac.uk/399818/1/paper_jgcd_preprint.pdf}{Gaussian process trajectories}}
\marginnote{\href{https://eprints.soton.ac.uk/363666/1/bluetoothHMM.pdf}{Hidden Markov model state estimation}}

In this research fellowship and lecturing role I focussed on simulation of traffic control and state estimation using machine learning methods. I also worked to secure over five-and-a-half million (USD equivalent) funding from multiple government grants and industrial collaborations to support this research. Additionally I taught Thermodynamics and Computer programming courses.

\subsection{2005-2007 Machine learning and perception group Microsoft Research}

\marginnote{\href{https://sourceforge.net/projects/camrocsim/}{Rocket simulator}}
\marginnote{\href{https://eprints.soton.ac.uk/73938/1/boxetal11\%2520\%25282\%2529.pdf}{Research paper}}
At Microsoft I developed a rocket flight simulator for unguided sounding rockets. This included modelling uncertainty in atmospheric data with a bespoke ML model described in the linked paper.

\section{Education}
\paragraph{2006 PhD, University of Cambridge}
Focussed on automotive modelling and simulation.
\paragraph{2002 MEng, Queen Mary, University of London}
Mechanical engineering
